\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-15 paper/draft.tex

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Synthetic Micro-benchmarks}.
		Applying the three analyses on a series of synthetic micro-benchmarks, created to stress different features.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
\toprule
              &   Base    &  SA     & PD       &   TIC    &   LSR     \\
\midrule
something1    &           &  0.70   &    3.43  &   3.46   &   3.26    \\
something2    &           &  1.31   &    4.81  &   4.55   &   4.63    \\
something3    &           &  5.95   &    4.78  &   4.25   &   4.85    \\
something4    &           &  18.29  &   11.20  &   10.24  &   9.54    \\
something5    &           &  24214  &   24721  &   24574  &   24502   \\
\bottomrule
\end{tabular*}
\label{tab:synthetic}
\vspace{-5mm}
\end{table}

>>>>

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Synthetic Micro-benchmarks}.
		Applying the three analyses on a series of synthetic micro-benchmarks, created to stress different features.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
\toprule
	      &   Base    &  SA     & PD      &  TIC    &  LSR \\
\midrule
something1    &   0.90    &  4.70   &  4.54   &  4.30   &  -   \\
something2    &   1.44    &  6.46   &  6.24   &  5.96   &  -   \\
something3    &   3.37    &  6.26   &  6.32   &  5.72   &  -   \\
something4    &   7.79    &  13.54  &  13.31  &  12.8   &  -   \\
something5    &   24661   &  24848  &  24754  &  24760  &  -   \\
something6    &   4.06    &  7.24   &  7.16   &  6.79   &  -   \\
something7    &   4.11    &  7.25   &  7.23   &  6.86   &  -   \\
something8    &   4.32    &  8.32   &  8.19   &  7.73   &  -   \\
\bottomrule
\end{tabular*}
\label{tab:synthetic}
\vspace{-5mm}
\end{table}
